---
title: "Demo AE"
  author: "insert name here"
format: html
editor: visual
---

For this ae, we'll use the **tidyverse** and **palmerpenguins** packages. Run the following code below. Further, name the code chunk `load-packages` using `#|`.

## Packages

```{r}
#| label: packages


library(tidyverse)
library(palmerpenguins) #The data set name is penguins
```

::: callout-note
Analyzing the a single variable is called **univariate** analysis.
:::

Before we begin, let's render the document.....

Why won't the document render? What does the error tell us? How do we fix the error?

**Add Response**

Now, fix the error and render the document. Are there messages / warnings from the packages code chunk that are not needed? Let's turn those off together as a class!


## Data

The dataset we will visualize is called `penguins`. Let's `glimpse()` at it by filling in the `...`.

```{r}
#| label: glimpse
#| eval: false

glimpse(...) #insert the name of the data set

```

# Visualizing penguin weights - Demo

## Useful links:

https://ggplot2.tidyverse.org/reference/

## Single variable

::: callout-note
Analyzing the a single variable is called **univariate** analysis.
:::

Create visualizations of the distribution of `weight`s of penguins.

1.  Make a histogram by filling in the `...` with the appropriate arguments. Set an appropriate binwidth.

```{r}
#| label: histogram-weight
#| eval: false

penguins |>
  ggplot( 
       aes(x = ...)) + #type variable name here
       ...(binwidth = 300) #type geom here

```

2.  Now, make a boxplot of `weight`s of penguins.

```{r}
#| label: boxplot-weight

# insert code here

```

::: callout-important
This would be a good time to render, commit, and push!
:::

-------------------------------- Answer for #2 Below

3.  Add a theme to your boxplot! https://ggplot2.tidyverse.org/reference/ggtheme.html

```{r}
#| label: theme

penguins |>
  ggplot(
    aes(x = body_mass_g)) + 
    geom_boxplot() # add a plus  
    # type theme here

```

**Add Response**

## Extensions

Make your own plot! Revist the geoms page here: https://ggplot2.tidyverse.org/reference/

```{r}
#| label: on-your-own

```
